---
title: "Week 12 R Home Learning Tasks"
author: "Kaycee"
date: "1/31/2022"
output: html_document
---
This is an Rmarkdown Document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Task 1:
Write an R program to create three vectors a, b, c with 5
integers. Combine the three vectors to become a 3×5 matrix
where each column represents a vector. Print the content of
the matrix. Plot a graph and label correctly.

```{r matrix}
a = c(1,2,3,4,5)
b = c(6,7,8,9,10)
c = c(11,12,13,14,15)
mat = matrix(c(a,b,c),
nrow = 3,
ncol =5)
print(mat)

# Plot the graph
plot(mat, type = "l", xlab = "X", ylab = "Y")

```

## Task 2:
Write a R program to create a Data frames which contain
details of 5 employees and display the details. (Name, Age,
Role and Length of service).



```{r employee}
# set vectors for name, age, role and length of service
emp_name = c("Scott", "Adam", "Chloe", "Kaycee", "Shawn")
age = c(21, 65, 45, 35, 50)
role = c("Nurse", "Radiographer", "Psychologist", "Phsyiotherapist", "Doctor")
len_service = c(6, 9, 8, 10, 25)

# create the dataframe 
employee = data.frame(emp_name, age, role, len_service)
print(employee)

```

Import the GGPLOT 2 library and plot a graph using the qplot
function. X axis is the sequence of 1:20 and the y axis is the x ^
2. Label the graph appropriately.

```{r ggplot}
# import library 
library(tidyverse)
# create sequence 1 to 20
x = seq(1,20)
y = x ^ 2
qplot(x,y, ylab = "X raised to power of 2")
```

Task 4
Create a simple bar plot of five subjects

```{r unordered barplot}
# lets create unordered barplot of employee and their age, we will use their role to fill the bar
employee %>% 
  ggplot(aes(emp_name, age, fill=role))+
  geom_bar(stat = "identity", show.legend = FALSE)+
  xlab("Name")+
  ylab("Age")+
  ggtitle("Unordered barplot of employee and their age")+
  theme_bw()
```

```{r ordered barplot}
# sort the barplot using fct_reorder
employee %>% 
  ggplot(aes(fct_reorder(emp_name, age),age, fill=role))+
  geom_bar(stat = "identity", show.legend = FALSE)+
  xlab("Name")+
  ylab("Age")+
  ggtitle("Ordered barplot of employee and their age")+
  theme_bw()
```

# Optional challenge

Write a R program to print the numbers from 1 to 100
and print "Fizz" for multiples of 3, print "Buzz" for
multiples of 5, and print "FizzBuzz" for multiples of
both.
```{r car}
for (i in 1:100){
  if(i %% 3 == 0 & i %% 5 == 0) {print("FizzBuzz")}
  else if(i %% 3 == 0) {print("Fizz")}
  else if(i %% 5 == 0) {print("Buzz")}
  else print(i)
}
```










